GMSE: a general tool for management strategy evaluation

### 2017-09-14 notebook/presentation/GMSE_presentation.Rmd
A bit more on the geese example

- Use some data from Jeremy's paper?

>>>>

- Wild geese declined starting in the 1930s, likely caused by habitat loss and increased hunting
- Refuges were established and hunting restricted in the 1950s, leading to recovery

[Fox & Madsen 2017 *Ambio* **46(s2)**:170-187](http://doi.org/10.1007/s13280-016-0878-2)
